Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-06-04 neurips-20/cvx-flats.tex
Added todo cal L
meeting notes

If given, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss}, with predictions $r\in\R$.
%where the goal is minimize expected loss, $\E ~ \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
A loss $\ell$ is \emph{discrete} if $\R$ is a finite set.
A surrogate $L$ is \emph{convex} if $L(\cdot,y)$ is convex for every label $y \in \Y$.
For a given $p\in\simplex$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.
\btw{Add note about minnability}
% For a distribution $p \in \simplex$, we denote the expected target loss for prediction $r$ to be $\E_{Y \sim p} \ell(r, Y) := \ell(r; p)$.
% Similarly, $\E_{Y \sim p} L(u, Y) := L(u ; p)$.

@@

Instead of a target loss $\ell$, one may want to learn a conditional statistic such as the expected value, variance, or entropy.
In this case, following the tradition in the statistics literature on conditional estimation~\citep{gyorfi2006distribution,fan1998efficient,ruppert1997local},
we formalize consistency as converging to the correct conditional estimates of the property.
Convergence is measured by functions $\propdis(r, p)$ that formalize how close $r$ is to ``correct'' for conditional distribution $p$.
In particular we should have $\propdis(r,p) = 0 \iff r \in \gamma(p)$.

@@

%commented out Jun 1 2020
%Theorem~\ref{thm:consistent-implies-indir-elic} allows us to use convex elicitation complexity as a tool to understand efficiency of consistent convex surrogates for a given property, which is more often what is given in a continuous estimation setting.
%For example, when one wants to learn an $\alpha$-quantile, we start with the property rather than a loss.
%In the literature, pinball loss $L(r,y) = (r-y)(\ones_{r \geq y} - \alpha)$ typically appears without explanation or justification as to why it is relevant in relation to the $\alpha$-quantile.
%Elicitation teaches us why pinball loss is consistent for learning a quantile as the pinball loss elicits the $\alpha$-quantile.
In continuous estimation problems, often one does not start with a target loss per se, but instead with a conditional statistic of the data one wishes to estimate, such as the conditional mean, variance, or entropy.
In this setting, Theorem~\ref{thm:cvx-flats} gives lower bounds on the prediction dimension of convex losses with a link to the desired conditional statistic, i.e., the convex elicitation complexity.
In particular, following an argument from~\citet{frongillo2018elicitation}, below Theorem~\ref{thm:bayes-risk-lower-bound} yields new bounds on the convex elicitation complexity of properties quantifying risk or uncertainty such as variance and entropy.
These bounds address an open question posed by~\citet{frongillo2018elicitation}, that of developing a theory of elicitation complexity for convex losses; our results show that not only is this theory possible, but the bounds thus far remain the same for convex losses.
\botodo{I didn't understand this precisely -- ``bounds remain the same for convex losses''. Can we phrase this more precisely/accurately? Also, should we mention 2agarwal here?}\jessiet{To my understanding: elicitation complexity of variance and entropy (which are identifiable) = convex elicitation complexity of var and entropy}
Extending to infinite $\Y$, such as $\Y=\reals$, remains open.

>>>>

If given, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss}, with predictions $r\in\R$.
%where the goal is minimize expected loss, $\E ~ \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
Similarly, $L: \reals^d \times \Y \to \reals$ will typically denote a \emph{surrogate} loss, with surrogate predictions $u \in \reals^d$.
A loss $\ell$ is \emph{discrete} if $\R$ is a finite set.
A surrogate $L$ is \emph{convex} if $L(\cdot,y)$ is convex for every label $y \in \Y$.
For a given $p\in\simplex$, the (conditional) \emph{regret}, or excess risk, of a loss $L$ is given by $R_L(u,p) := \exploss{L}{u}{p} - \inf_{u^*} \exploss{L}{u^*}{p}$.

\botodo{Define calligraphic L, L sub d for dimension d.}

\btw{Add note about minnability}
% For a distribution $p \in \simplex$, we denote the expected target loss for prediction $r$ to be $\E_{Y \sim p} \ell(r, Y) := \ell(r; p)$.
% Similarly, $\E_{Y \sim p} L(u, Y) := L(u ; p)$.

@@

Instead of a target loss $\ell$, one may want to learn a conditional statistic such as the expected value, variance, or entropy.
In this case, following the tradition in the statistics literature on conditional estimation~\citep{gyorfi2006distribution,fan1998efficient,ruppert1997local},
we formalize consistency as converging to the correct conditional estimates of the property.
Convergence is measured by functions $\propdis(r, p)$ that formalize how close $r$ is to ``correct'' for conditional distribution $p$.
In particular we should have $\propdis(r,p) = 0 \iff r \in \gamma(p)$.
\btw{Bo: Would be nice to give some natural special cases: for a finite property, $\propdis(r,p) = \mathbf{1}[r \in \gamma(p)]$, and for single-valued properties with a distance metric on $\R$, $\propdis(r,p) = \text{dist}(r, \gamma(p))$.}

@@

%commented out Jun 1 2020
%Theorem~\ref{thm:consistent-implies-indir-elic} allows us to use convex elicitation complexity as a tool to understand efficiency of consistent convex surrogates for a given property, which is more often what is given in a continuous estimation setting.
%For example, when one wants to learn an $\alpha$-quantile, we start with the property rather than a loss.
%In the literature, pinball loss $L(r,y) = (r-y)(\ones_{r \geq y} - \alpha)$ typically appears without explanation or justification as to why it is relevant in relation to the $\alpha$-quantile.
%Elicitation teaches us why pinball loss is consistent for learning a quantile as the pinball loss elicits the $\alpha$-quantile.
In continuous estimation problems, often one does not start with a target loss per se, but instead with a conditional statistic of the data one wishes to estimate, such as the conditional mean, variance, or entropy.
In this setting, Theorem~\ref{thm:cvx-flats} gives lower bounds on the prediction dimension of convex losses with a link to the desired conditional statistic, i.e., the convex elicitation complexity.
In particular, following an argument from~\citet{frongillo2018elicitation}, below Theorem~\ref{thm:bayes-risk-lower-bound} yields new bounds on the convex elicitation complexity of properties quantifying risk or uncertainty such as variance and entropy.
These bounds address an open question posed by~\citet{frongillo2018elicitation}, that of developing a theory of elicitation complexity for convex losses;
\raft{for cts pred}
our results show that not only is this theory possible, but the bounds thus far remain the same for convex losses.
\raft{complexity wrt surrogates they consider}
\botodo{I didn't understand this precisely -- ``bounds remain the same for convex losses''. Can we phrase this more precisely/accurately? Also, should we mention 2agarwal here?}\jessiet{To my understanding: elicitation complexity of variance and entropy (which are identifiable) = convex elicitation complexity of var and entropy}
Extending to infinite $\Y$, such as $\Y=\reals$, remains open.
